\large{\bf Looking forwards and backwards: dynamics and genealogies of locally regulated populations }

### 2023-05-23 forwards-and-backwards.tex
.

We follow the approach of Lemma~\ref{lem:eta_compact_containment}.
Consulting~\eqref{eqn:prelimit_martingale_variation},
the angle bracket process of $\widehat{M}^N(f)$ satisfies
$ \IE[\langle\widehat{M}^N_f\rangle_T] \le C (\theta/N) \int_0^T \IE[\langle 1, \eta_s \rangle] ds \le C' \theta/N$
for some constants $C$ and $C'$.
Now, using the Burkholder-Davis-Gundy inequality and \citet{hernandez/jacka:2022},
$\IE[\sup_{0 \le u \le T} |\widehat{M}^N(f)_u|^2] \le C'' \IE[\langle\widehat{M}^N(f)\rangle_u]$,
and so using Markov's inequality,
\begin{equation}
\label{martingale term to zero}
    \limsup_{N\to\infty}\IP\Big[
        2\sup_{0\leq u\leq T}|\widehat{M}^N(f)_u|
        >\frac{\nu}{3}
    \Big]
    \leq
    \limsup_{N\to\infty} \frac{36}{\nu^2} C'' \IE\big[\langle\widehat{M}^N(f)\rangle_T\big]
    \leq
    \limsup_{N\to\infty}\frac{36}{\nu^2}\frac{C' C''\theta}{N\epsilon^d} 
    =0. 
\end{equation}

>>>>

We follow the approach of Lemma~\ref{lem:eta_compact_containment}.
Consulting~\eqref{eqn:prelimit_martingale_variation},
the angle bracket process of $\widehat{M}^N(f)$ satisfies
$ \IE[\langle\widehat{M}^N_f\rangle_T] \le C (\theta/N) \int_0^T \IE[\langle 1, \eta_s \rangle] ds \le C' \theta/N$
for some constants $C$ and $C'$.
Now, using the Burkholder-Davis-Gundy inequality and \citet{barlow/jacka/yor:1986},
$\IE[\sup_{0 \le u \le T} |\widehat{M}^N(f)_u|^2] \le C'' \IE[\langle\widehat{M}^N(f)\rangle_u]$,
and so using Markov's inequality,
\begin{equation}
\label{martingale term to zero}
    \limsup_{N\to\infty}\IP\Big[
        2\sup_{0\leq u\leq T}|\widehat{M}^N(f)_u|
        >\frac{\nu}{3}
    \Big]
    \leq
    \limsup_{N\to\infty} \frac{36}{\nu^2} C'' \IE\big[\langle\widehat{M}^N(f)\rangle_T\big]
    \leq
    \limsup_{N\to\infty}\frac{36}{\nu^2}\frac{C' C''\theta}{N\epsilon^d} 
    =0. 
\end{equation}
